%Paragraph formatting
	%\setlength{\parskip}{12pt}
	\setstretch{1.5}
	\raggedright

%Essay Heading
	\today \\[12pt] Graduate Admission Committee \\ Halıcıoğlu Data Science Institute \\[24pt]

%Title
	%\centerline{Statement of Purpose}

%Development

% * WHAT TO ANSWER ON THE Statement of Purpose: 
% * 	According to HDSI Grad Admission: 
% * There is no specific word limit, but be concise and specific in preparing your statement, 
% * giving information that demonstrates your level of preparation and potential for success in graduate school.

% * 	According to the UCSD Grad Admission:
% * Focus your Statement of Purpose on the reasons you are interested in attending a specific graduate program at UCSD. 
% * Check the department requirements for the Statement of Purpose. The statement should be well organized, concise, 
% * and completely free of grammar, punctuation, and spelling errors. Before submitting the statement, seek constructive 
% * comments and criticism from friends and advisors.

% *		PRIMARY FACTORS
% * 	1. How did you become interested in this field? 
% * 	2. What experiences have contributed toward your preparation for further study in this field?
% * 	3. What are your future goals? Specifically state your degree objective (Master's or Ph.D.) and specify what subdisciplines...
% * 	4. What are your research interests?
% * 	5. How are you a "match" for the program to which you are applying?

% *		SECONDARY FACTORS:
% *		• Give examples of personal attributes or qualities that would help you complete graduate study successfully.
% *		• Describe your determination to achieve your goals, your initiative and ability to develop ideas, and your ability to work independently.
% *		• Describe background characteristics that may have placed you at an educational disadvantage (English language learner, family economic history, lack of educational opportunity, disability, etc.).
% *		• Leave the reader believing that you are prepared for advanced academic work and will be successful in graduate school.

% * MORE INFO: https://grad.ucsd.edu/admissions/requirements/statement-of-purpose.html

% TODO: WRITE THE FOURTH DRAFT; now ask ChatGPT for writing checks and extras!!!
% TODO: comment any possible corrections and/or changes with the "Better Comments" format
	\noindent
	Many software developers coin the term “Perpetual Beta” to a software product that's improved upon but 
	never published as an official release. In the philosophy of Stoicism, there is an endless cycle of improvement 
	and the embracing of discomfort because it articulates that hardship makes us stronger. These two views of different 
	fields of knowledge have been the main drivers of my work ethic, given the fact that they embrace whatever the game 
	of life decides against us or in favor of us. As long as I remember, my drive for learning as a whole began with 
	reading a collection of children's themed encyclopedias with the characters of Peanuts, and from there, a search for 
	further knowledge by pursuing a college degree.
	
	\setlength{\parindent}{.3in}
	  
	During my undergraduate lectures, I initially found them underwhelming. However, the COVID-19 pandemic offered a unique opportunity 
	for reflection within the context of history. This period spurred a personal transformation, fueling a stronger drive for self-improvement. 
	Amid the turbulence, I embraced physical fitness and enhanced my analytical skills by studying academic papers. Eventually, these
	personal interests molded me into a proud and ambitious individual, eager for continuous growth. In the seventh semester
	of my undergrad, we got the opportunity to write a proper academic research paper, which made me consider the realms of 
	research as an entire professional career when it felt that I was experiencing an analysis paralysis about my future outside of undergrad.
	
	Fast forward to Summer 2023, I got the opportunity to be one of the many promising students of the prestigious ENLACE 2023 Summer 
	Research Program, and a glimpse into the realms of academic research that solidified my resolute to pursue higher education to 
	fulfill my dreams and goals of moving knowledge forward, making me feel like a child with every new interaction that we 
	had with our mentors and colleagues about their respective academic domains. The project that was developed in the
	camp relates drastically to the type of labor that is Data Science; we were tasked to train a DNN with Pytorch and 
	get the performance plots and statistics to determine if the model could compete against a GNN that was trained for particle
	tracking at the Large Hadron Collider, and we found that the simplicity of a DNN could be as accurate as the GNN, which was a surprising
	result to everyone involved. I never thought that a single project done in one summer could affect my worldview so 
	drastically that it convinced me to pursue a graduate degree in Data Science. Given this, to become
	a student of the Halıcıoğlu Data Science Institute and its graduate program on Data Science would be an honor.
	
	For many, the world-renowned rigor of American Academia can be daunting, but for me, it is necessary to mold better individuals capable 
	of proper academic research and reasoning in every other aspect of life. This is why pursuing a Ph.D. in Data Science would assist
	my career. With this, I am truly committed to this academic journey, the University of California San Diego, and the Halıcıoğlu
	Data Science Institute, and the community itself. 
	
	Although I've yet to have the pleasure and honor to meet the faculty members, the research focus of Berk Ustun, David Banks, 
	Mikhail Belkin & Vineet Bafna is of utmost interest given the fact that they are working with the theoretical aspects
	of Data Science, the applications of Data Science to support science and medicine. With the former, if my acceptance is
	considered, I would be very pleased if I could work on high-dimensional data with Machine Learning models and research
	related to the applications of Data Science for the understanding, and even the treatment of various skin 
	conditions. I am convinced that a solid theoretical background can lay down more successful applicated projects, 
	and because I too have dealt with several skin conditions such as Cystical Hormonal Acne, these reasons
	are enough drive to dedicate myself to the realms of academia and have a chance to write research
	that can help others to comprehend the complex and marvelous theory of Machine Learning models and
	to treat such skin conditions, and all of this in the reputable institution of the UCSD and the Halıcıoğlu Data Science Institute.
